A Type System for String Sanitation\\Implemented Inside a Python

### 2014-08-05 sanitation-psp14/sanitation-psp14-short.tex
Adding short version.

A number of research languages provide static guarantees that a program is free of input sanitation vulnerabilities [Jif][Ur/Web]. Our work differes from these contributions in the ways following:

\begin{itemize}
  \item Our system is a light-weight solution to a single class of sanitation vulnerabilities (e.g. we do not address Cross-Site Scripting).
  \item Our system is defined as a library in terms of an extensible type system, as opposed to a stand-alone language. Instead of introducing new technologies and methodologies for addressing security problems, we provide a light-weight static analysis which complements approaches developers already understand well.
  \item Our implementation of the translation is implemented in Python and shares its grammar. Since Python is a popular programming language among web developers, the barrier between our research and adopted technologies is lower than for greenfield security-oriented languages.
\end{itemize}

@@

\subsection{Outline}

An outline of this paper follows:

\begin{itemize}
  \item In \S 2, we define the type system which is embedded in Ace. We include a type safety proof for the string
    segment of this language and prove the correctness of a translation to an underlying langguage $P$. In our theory,
    $P$ is a simply typed lambda calculus equipped with a minimal regular expression library; in an implementation, $P$
    stands in for Python or another underlying general-purpose programming language.
  \item In \S 3, we discuss our implemention of this translation as a type system extension  within the Ace programming language.
\end{itemize}

@@

The system $\lambdas$ \ref{fig:lambdas} is the simply typed lambda calculus extended with \emph{regular expression types}, which are string
types ensuring a string belongs to a specified language. For instance, 
$S : \stringin{r}$ reads ``$s$ is a string matching $r$".
the system includes an operation for replacing all instances of a pattern $r$ in a string $s_1$ with another string $s_2$. 
Input sanitation algorithms -- as implemented by developers or within popular libraries and frameworks -- are often implemented in terms of this replace operation.
For instance, a developer might all potentially unsafe charapcters with excaped versions of the same character.
Regular expression types are used both to specify input sanitation algorithms, and at use sites as specifications.
Note that runtime error states ($S \err$) are introduced by coercion, not by replacement.

The language $\lambdap$ \ref{fig:lambdap} is a simple functional language extended with a minimal regular expression library.
Any general purpose programming language could stand in for $\lambdap$; for instance, SML has a regular expression library.
In an implementation, our correctness results are modulo the underlying language's correct implementation of regular expression matching (see P-E-Replace).

Finally, we define a translation from our type system $\lambdas$ into $\lambdap$.

%Note that we never insert an internal check where the type of the string implies
%that a check must succeed. Furthermore, expensive calculations (such as language
%inclusion or ${\sf rreplace}$) all occur at compile time.
%Since sanitation problems are generally expressible with smalle, simple expressions,
%we believe that the compile-time overhead is not significant enough to prohibiour target usecase. Informal experimentation with our implementation seems to
%support this assertion.

@@

Our type safety proofs for languages S and P and our translation correctness
result all depend on some properties of regular languages. The crucial property
is a relationship between string substitution -- which is available in any regular
expression library -- and regular language substitution, which is a corresponding operation
on languages instead of strings \ref{thm:substcorrespondence}.
The decidability of language substitution is what enables static analysis of 
sanitation algorithms implemented in terms of string replacement

Throughout this section, we fix an alphabet $\Sigma$ over which strings $s$ and
regular expressions $r$ are defined. throughout the paper, $\lang{r}$ refers to the
language recognized by the expression $r$. This distinction between the expression
and its language -- typically elided in the literature -- makes our definition and
proofs about systems S and P more readable.

\begin{lem}{Properties of Regular Languages and Expressions.} \label{thm:regexprops}
The following are well-known properties of regular expressions which are necessary for our proofs:
\begin{description}
\item[(1):] If $s_1 \in \lang{r_1}$ and $s_2 \in \lang{r_2}$ then $s_1s_2 \in \lang{r_1r_2}$
\item[(2):] For all strings $s$ and expressions $r$, either $s \in \lang{r}$ or $s \not \in \lang{r}$.
\item[(3):] Regular languages are closed under complements and concatenation.
\item[(4):] The regular expressions correspond bijectively to the regular languages.
\end{description}
\end{lem}

@@

\begin{lem}{Substitution Correspondence.} \label{thm:substcorrespondence}
If $s_1 \in \lang{r_1}$ and $s_2 \in \lang{r_2}$ then $\lsubst{r}{s_1}{s_2} \in \lreplace{r}{r_1}{r_2}$.
\end{lem}
\begin{proof}
The proof proceeds by structural induction on $r$.

\begin{description}
\item[case $r=\alpha$.]
If $s_1 = \alpha$ then $\alpha \in \lang{r_1}$ by assumption.
Therefore, $\lsubst{r}{s_1}{s_2} = \lsubst{\alpha}{\alpha}{s_2} = s_2$ and
$\lreplace{r}{r_1}{r_2} = \lreplace{\alpha}{r_1}{r_2}$. 
Since $s_1 = \alpha$ and $\alpha \in \lang{r_1}$, $r_1 \iso \alpha | r_1'$ for some $r_1'$.
Therefore, $\lreplace{\alpha}{r_1}{r_2} \iso \lreplace{\alpha}{\alpha|r_1'}{r_2}$ by Lemma X(1).
Finally, $s_2 \in \lang{r_2}$ which implies $s_1 \in \lang{r_2|r'}$.
If $s_1 \not = \alpha$ the $\lsubst{r}{s_1}{s_2} = s_1$ and $\lreplace{\alpha}{r_1}{r_2} = r_1$.

\item[case $r = a|b$].
Note that $\subst{a|b}{s_1}{s_2} = \lsubst{a}{\lsubst{b}{s_1}{s_2}}{s_2}$
and $\lsubst{b}{s_1}{s_2} \in \lreplace{b}{r_1}{r_2}$ by induction.
Therefore, $\lsubst{a|b}{s_1}{s_2}$ $\in \lreplace{a}{\lreplace{b}{r_1}{r_2}}{r_2}$ by induction and the definition of lreplace.
Finally, applying definitions once more, $\lsubst{a|b}{s_1}{s_2} \in \lreplace{a|b}{r_1}{r_2}$.

\item[case $r = ab$].
By a similar argument to the disjunctive case.

\item[case $r = a*$].
By considering the once unwinding of $a*$, noting that $s_1$ and $s_2$ are finite.
\end{description}
\end{proof}

@@

\begin{lem}
  If $\sctx \vdash S : \stringin{r}$ then $r$ is a well-formed regular expression. 
\end{lem}
\begin{proof}
  The only non-trivial case is S-T-Replace, which follows from \ref{thm:total}. 
\end{proof}

@@

\begin{thm}{Safety for the String Fragment of P.}
  Let $S$ be a term in the source language. If $\sctx \vdash S : \stringin{r}$ 
  then $S \sreduces \rstr{s}$ and $\rstr{s} : \stringin{r}$, or else $S \err$.
\end{thm}
\begin{proof}
By induction on the derivation of $\sctx \vdash S : \psi$. The interesting case
is S-T-Replace, which requires Lemma C.

\begin{description}
\item[S-T-Stringin-I:]
If $S = \rsconcat{S_1}{S_2} : \stringin{r}$ then
$S \sreduces S$ by S-E-RStr, and $\sctx \vdash S : \psi$ by assumption.

\item[S-T-Concat:] 
Suppose $S = \rsconcat{S_1}{S_2} : \stringin{r_1 r_2}$.
By inversion, $\sctx \vdash S_1 : \stringin{r_1}$ and $\sctx \vdash S_1 : \stringin{r_2}$.
It follows by induction that either $S_1 \err$, $S_2 \err$, 
or $S_1 \sreduces \rstr{s_1}$ and $S_2 \sreduces \rstr{s_2}$ for some $s_1 \in \lang{r_1}$ and $s_2 \in \lang{r_2}$.
In the latter case $S \reduces \rstr{s_1s_2}$ by S-E-Concat and $\sctx \vdash \rstr{s_1s_2} : \tstr{r_1r_2}$ by \ref{thm:regexprops}.
In the former cases, $S \err$.

\item[S-T-Replace:]
Suppose $S = \rreplace{r}{S_1}{S_2}$ and $\sctx \vdash S : \stringin{r'}$.
By inversion $\sctx \vdash S_1 : \stringin{r_1}$ and $\sctx \vdash S_2 : \stringin{r_2}$ such that $\lsubst{r}{r_1}{r_2} = r'$.
By induction, $S_1 \err$, $S_2 \err$ 
or $S_1 \sreduces \rstr{s_1}$ and $S_2 \sreduces \rstr{s_2}$ such that 
In the latter case, we know $\lreplace{r}{s_1}{s_2} \in \lang{\lsubst{r}{r_1}{r_2}}$ by Lemma C;
therefore by S-E-Replace, $S \sreduces \rstr{s}$ such that  $s \in \lang{\lsubst{r}{r_1}{r_2}} = \lang{r'}$.
So by S-T-String-I, $\rstr{s} : \stringin{r'}$.
In the former cases, $S \err$.

\item[S-T-Coerce:]
Suppose $S = \coerce{r}{S_1}$ and $S : \stringin{r}$.
By inversion, $\sctx \vdash S_1 : \stringin{r'}$.
By induction, $S_1 \err$ or $S_1 \sreduces \rstr{s}$.
In the former case $S \err$ by propagation rules.
In the latter case we have by property 2 of \ref{thm:regexprops} that $s \in \lang{r}$ or else
$s \not \in \lang{r}$.
If $s \in \lang{r}$ then $\rstr{s} : \stringin{r}$.
If $s \not \in \lang{r}$ then $S \err$. 
\end{description}
\end{proof}

\begin{thm}
  Let $P$ be a term in the target language. If $\tctx \vdash P : \theta$ 
  then $P \sreduces P'$ and $P' : \theta$.
\end{thm}
\begin{proof}
The proof proceeds by induction on the typing relation and is trivial give
and inversion lemma for the typing relation. \textbf{We can write up this proof if we end up having enough space...}
\end{proof}

@@

\begin{thm}
If $S : \strin{r}$ then there exists a P such that $\trden{s} = P$ and either: 
\begin{description}
  \item[(a)] $P \treduces \tstr{s}$ and $S \sreduces \strin{s}$, and $s \in lang{r}$.
  \item[(b)] $P \err$ and $S \err$.
  \end{description}
\end{thm}

\begin{proof}
The proof proceeds by induction on the typing relation for $S$.
Throughout the proof, properties from the closure lemma for regular languages
are necessary; for brevity, we elide these references.

\begin{description}
\item[S-T-String-I:] 
Let $S = \rstr{s}$ and suppose $\sctx \vdash \rstr{s} : \stringin{r}$.
Choose $T = \str{s}$ and note that $\trden{S} = P$ by Tr-String.
By P-E-String, $P \treduces \str{s}$ and by S-E-String $S \treduces \rstr{s}$.
Finally, by inversion of S-T-Stringin-I, $s \in \lang{r}$.

\item[S-T-Concat:]
Let $S = \rconcat{S_1}{S_2}$ and suppose $\sctx \vdash S : \stringin{r_1 r_2}$.
By inversion, $\sctx \vdash S_1 : \stringin{r_1}$.
It follows by induction that there exists a $P_1$ such that $\trden{S_1} = P_1$.
By a similar argument for $S_2$ and $r_2$, there exists a $P_2$ such that $\trden{S_2} = P_2$.
Choose $P = \concat{P_1}{P_2}$.

We first prove property (a).
Note that $S_1$ and $P_1$ are well typed (nrf ACTUALLY WE DON'T KNOW THAT $P_1$ IS WELL-TYPED!) and do not result in errors.
Therefore, $S_1 \sreduces \rstr{s_1}$ and $P_1 \treduces \str{s_1}$ for some $s_1 \in \lang{r_1}$ by theorems 8 and 9 respectively. % TODO-nrf make sure this numbering is correct
Similarly, $S_2 \sreduces \rstr{s_2}$ and $P_2 \treduces \str{s_2}$ for some $s_2 \in \lang{r_2}$.
Therefore, $S \sreduces \rstr{s_1 s_2}$ by S-E-Concat and $\concat{P_1}{P_2} \treduces \str{s_1 s_2}$ by P-E-Concat.
Finally, $s_1s_2 \in \lang{r_1}{r_2}$ by \ref{thm:regexprops}.

Consider property (b).
If $S_1 \err$ then $P_1 \err$ by induction, and it follows that $S \err$ and $P \err$ by respective error propagation rules.
Similarly, if $S_2 \err$ then $P_2 \err$ and it follow that $S \err$ and $P \err$ by induction and propagation.

\item[S-T-Replace:]
Let $S = \rreplace{r}{S_1}{S_2}$ and suppose $\sctx \vdash S : \stringin{r'}$ for some $s$.
By inversion of S-T-Replace, , $\sctx S_1 : \stringin{r_1}$ and $\sctx : \stringin{r_2}$ 
such that $\lsubst{r}{r_1}{r_2} = r'$.
By induction, there exists some $P_1, P_2$ such that $\trden{S_1} = P_1$, $\trden{S_2} = P_2$
and either (a) or (b) holds.

If (a) holds then $S_1 \sreduces \rstr{s_1}$ and $P_1 \treduces \str{s_1}$ for some $s_1 \in \lang{r_1}$,
and similarly for $S_2, P_2$ and some $s_2 \in \lang{r_2}$.
Therefore, by S-E-Replace, $S \sreduces \rstr{s}$ for some $s = \lreplace{r}{s_1}{s_2}$.
Choose $P = \preplace{r}{s_1}{s_2}$.
By a similar argument and P-E-Replace, $P \treduces \str{s}$ for some $s = \lreplace{r}{s_1}{s_2}$.
What remains to be shown is $\lreplace{r}{s_1}{s_2} \in \lang{\lsubst{r}{r_1}{r_2}}$,
which follows from Leamm D since $s_1 \in r_1$ and $s_2 \in r_2$.

If (b) holds for $S_1$ and $P_1$, then $S \err$ and $P \err$ by propagation rules.
Similarly, if (b) hols for $S_2$ and $P_2$ then $S \err$ and $P \err$ by propagation rules.

\item[S-T-Coerce:]
Let $S = \rcoerce{r}{S'}$ and suppose $\sctx \vdash \rcoerce{r}{S} : \stringin{r}$.
By inverstion $\Psi \vdash S' : \stringin{r'}$ for an arbitrary $r'$.
By induction there exists a $P'$ such that $\trden{S'} = P'$ and either (a) or (b)
holds for $S'$ and $P'$.

If (a) holds then $S' \sreduces \rstr{s'}$ and $P' \treduces \str{s'}$ for some $s' \in \lang{r'}$.
Note that either $s' \in \lang{r}$ or $s' \not \in \lang{r}$ by property 2 of \ref{thm:regexprops}.
Suppose $s' \in \lang{r}$. Then $\rcoerce{r}{S} \sreduces \rstr{S'}$ by S-E-Coerce.
Choose $P = \check{\rx{r}}{P'}$ and note that $P \treduces \str{s'}$ by P-E-Coerce.
Now suppose $s' \not \in \lang{r}$. Then $S \err$ and $P \err$ by P-E-Check-Err
and S-E-Coerce-Err.

Finally, if (b) holds then $S \err$ and $P \err$ by propagation.

\end{description}
\end{proof}

@@

>>>>

A number of research languages provide static guarantees that a program is free of input sanitation vulnerabilities [Jif][Ur/Web]. 
Unlike this work, our solution to the input sanitation problem has a very low barrier to adoption; for instance, our implementation conservatively extends Python -- a popular language among web developers.
We also believe our general approach is better-positioned for security, where continuously evolving threats might require frequent addition of new analyses; in these cases, the composability and generality of our approach is a substantial advantage.

%\begin{itemize}
%  \item Our system is a light-weight solution to a single class of sanitation vulnerabilities (e.g. we do not address Cross-Site Scripting).
%  \item Our system is defined as a library in terms of an extensible type system, as opposed to a stand-alone language. Instead of introducing new technologies and methodologies for addressing security problems, we provide a light-weight static analysis which complements approaches developers already understand well.
%  \item Our implementation of the translation is implemented in Python and shares its grammar. Since Python is a popular programming language among web developers, the barrier between our research and adopted technologies is lower than for greenfield security-oriented languages.
%\end{itemize}

@@

%\subsection{Outline}
%
%An outline of this paper follows:
%
%\begin{itemize}
%  \item In \S 2, we define the type system which is embedded in Ace. We include a type safety proof for the string
%    segment of this language and prove the correctness of a translation to an underlying langguage $P$. In our theory,
%    $P$ is a simply typed lambda calculus equipped with a minimal regular expression library; in an implementation, $P$
%    stands in for Python or another underlying general-purpose programming language.
%  \item In \S 3, we discuss our implemention of this translation as a type system extension  within the Ace programming language.
%\end{itemize}

@@

The system $\lambdas$ is the simply typed lambda calculus extended with \emph{regular expression types}, which are string
types ensuring a string belongs to a specified language. For instance, 
$S : \stringin{r}$ reads ``$s$ is a string matching $r$".
the system includes an operation for replacing all instances of a pattern $r$ in a string $s_1$ with another string $s_2$. 
Input sanitation algorithms -- as implemented by developers or within popular libraries and frameworks -- are often implemented in terms of this replace operation.

The language $\lambdap$ is a simple functional language extended with a minimal regular expression library.
Any general purpose programming language could stand in for $\lambdap$; for instance, SML or Python.
In an implementation, our correctness results are modulo the underlying language's correct implementation of regular expression matching (see P-E-Replace).

Finally, we define a translation from our type system $\lambdas$ into $\lambdap$ which preserves the safety guarnatee codified in the string types of $\lambdas$. Because our extension is conservative and its guarnatees are preserved under translation to an underlying language, it is highly composable with other analyses.

Unfortunately, we are unable to present full proofs here due to space constraints.
%Note that we never insert an internal check where the type of the string implies
%that a check must succeed. Furthermore, expensive calculations (such as language
%inclusion or ${\sf rreplace}$) all occur at compile time.
%Since sanitation problems are generally expressible with smalle, simple expressions,
%we believe that the compile-time overhead is not significant enough to prohibiour target usecase. Informal experimentation with our implementation seems to
%support this assertion.

@@

Our type safety proof for language S replies on a relationship between
string substitution and language substitution given in lemma \ref{thm:substcorrespondence}.
We also rely upon several other properties of regular languages.
Throughout this section, we fix an alphabet $\Sigma$ over which strings $s$ and
regular expressions $r$ are defined. throughout the paper, $\lang{r}$ refers to the
language recognized by the expression $r$. This distinction between the expression
and its language -- typically elided in the literature -- makes our definition and
proofs about systems S and P more readable.

\begin{lem}{Properties of Regular Languages and Expressions.} \label{thm:regexprops}
The following are well-known properties of regular expressions which are necessary for our proofs:
If $s_1 \in \lang{r_1}$ and $s_2 \in \lang{r_2}$ then $s_1s_2 \in \lang{r_1r_2}$.
For all strings $s$ and expressions $r$, either $s \in \lang{r}$ or $s \not \in \lang{r}$.
Regular languages are closed under complements and concatenation.
The regular expressions correspond bijectively to the regular languages.
\end{lem}

@@

\begin{lem}{Substitution Correspondence.} \label{thm:substcorrespondence}
If $s_1 \in \lang{r_1}$ and $s_2 \in \lang{r_2}$ then $\lsubst{r}{s_1}{s_2} \in \lang{\lreplace{r}{r_1}{r_2}}$.
\end{lem}
\begin{proof}
The proof proceeds by structural induction on $r$.
The base case ($r=\alpha, \alpha \in \Sigma$) is trivial.
The choice and sequential cases require lemma 1, and prove a more general property that $\lsubst{r}{s_1}{s_2} \in \lang{r'}$ for some $r'$ isomorphic to $\lreplace{r}{r_1}{r_2}$.
The closure case follows from the induction hypothesis applied to any $n$-unwinding.

%\begin{description}
%\item[case $r=\alpha$.]
%If $s_1 = \alpha$ then $\alpha \in \lang{r_1}$ by assumption.
%Therefore, $\lsubst{r}{s_1}{s_2} = \lsubst{\alpha}{\alpha}{s_2} = s_2$ and
%$\lreplace{r}{r_1}{r_2} = \lreplace{\alpha}{r_1}{r_2}$. 
%Since $s_1 = \alpha$ and $\alpha \in \lang{r_1}$, $r_1 \iso \alpha | r_1'$ for some $r_1'$.
%Therefore, $\lreplace{\alpha}{r_1}{r_2} \iso \lreplace{\alpha}{\alpha|r_1'}{r_2}$ by Lemma X(1).
%Finally, $s_2 \in \lang{r_2}$ which implies $s_1 \in \lang{r_2|r'}$.
%If $s_1 \not = \alpha$ the $\lsubst{r}{s_1}{s_2} = s_1$ and $\lreplace{\alpha}{r_1}{r_2} = r_1$.
%
%\item[case $r = a|b$].
%Note that $\subst{a|b}{s_1}{s_2} = \lsubst{a}{\lsubst{b}{s_1}{s_2}}{s_2}$
%and $\lsubst{b}{s_1}{s_2} \in \lreplace{b}{r_1}{r_2}$ by induction.
%Therefore, $\lsubst{a|b}{s_1}{s_2} \in \lreplace{a}{\lreplace{b}{r_1}{r_2}}{r_2}$ by induction and the definition of lreplace.
%Finally, applying definitions once more, $\lsubst{a|b}{s_1}{s_2} \in \lreplace{a|b}{r_1}{r_2}$.
%
%\item[case $r = ab$].
%By a similar argument to the disjunctive case.
%
%\item[case $r = a*$].
%By considering the once unwinding of $a*$, noting that $s_1$ and $s_2$ are finite.
%\end{description}
\end{proof}

@@

\begin{lem}
  If $\sctx \vdash S : \stringin{r}$ then $r$ is a well-formed regular expression. 
\end{lem}
\begin{proof}
  The only non-trivial case is S-T-Replace, which follows from lemma \ref{thm:total}. 
\end{proof}

@@

\begin{thm}{Safety for the String Fragment of P.}
  Let $S$ be a term in the source language. If $\sctx \vdash S : \stringin{r}$ 
  then $S \sreduces \rstr{s}$ and $\rstr{s} : \stringin{r}$, or else $S \err$.
\end{thm}
\begin{proof}
By induction on the derivation of $\sctx \vdash S : \psi$. The interesting case
is S-T-Replace, which requires lemma \ref{thm:substcorrespondence}. The 
Coercion lemma additionally requires the second property of lemma \ref{thm:regexprops}.

%\begin{description}
%\item[S-T-Stringin-I:]
%If $S = \rsconcat{S_1}{S_2} : \stringin{r}$ then
%$S \sreduces S$ by S-E-RStr, and $\sctx \vdash S : \psi$ by assumption.
%
%\item[S-T-Concat:] 
%Suppose $S = \rsconcat{S_1}{S_2} : \stringin{r_1 r_2}$.
%By inversion, $\sctx \vdash S_1 : \stringin{r_1}$ and $\sctx \vdash S_1 : \stringin{r_2}$.
%It follows by induction that either $S_1 \err$, $S_2 \err$, 
%or $S_1 \sreduces \rstr{s_1}$ and $S_2 \sreduces \rstr{s_2}$ for some $s_1 \in \lang{r_1}$ and $s_2 \in \lang{r_2}$.
%In the latter case $S \reduces \rstr{s_1s_2}$ by S-E-Concat and $\sctx \vdash \rstr{s_1s_2} : \tstr{r_1r_2}$ by \ref{thm:regexprops}.
%In the former cases, $S \err$.
%
%\item[S-T-Replace:a]
%Suppose $S = \rreplace{r}{S_1}{S_2}$ and $\sctx \vdash S : \stringin{r'}$.
%By inversion $\sctx \vdash S_1 : \stringin{r_1}$ and $\sctx \vdash S_2 : \stringin{r_2}$ such that $\lsubst{r}{r_1}{r_2} = r'$.
%By induction, $S_1 \err$, $S_2 \err$ 
%or $S_1 \sreduces \rstr{s_1}$ and $S_2 \sreduces \rstr{s_2}$ such that 
%In the latter case, we know $\lreplace{r}{s_1}{s_2} \in
%\lang{\lsubst{r}{r_1}{r_2}}$ by lemma \ref{thm:substcorrespondence};
%therefore by S-E-Replace, $S \sreduces \rstr{s}$ such that  
%
%$s \in \lang{\lsubst{r}{r_1}{r_2}} = \lang{r'}$.
%So by S-T-String-I, $\rstr{s} : \stringin{r'}$.
%In the former cases, $S \err$.
%
%\item[S-T-Coerce:]
%Suppose $S = \coerce{r}{S_1}$ and $S : \stringin{r}$.
%By inversion, $\sctx \vdash S_1 : \stringin{r'}$.
%By induction, $S_1 \err$ or $S_1 \sreduces \rstr{s}$.
%In the former case $S \err$ by propagation rules.
%In the latter case we have by property 2 of \ref{thm:regexprops} that $s \in \lang{r}$ or else
%$s \not \in \lang{r}$.
%If $s \in \lang{r}$ then $\rstr{s} : \stringin{r}$.
%If $s \not \in \lang{r}$ then $S \err$. 
%\end{description}
\end{proof}

\begin{thm}
  Let $P$ be a term in the target language. If $\tctx \vdash P : \theta$ 
  then $P \sreduces P'$ and $\tctx \vdash P' : \theta$.
\end{thm}

@@

\begin{thm}
If $S : \strin{r}$ then there exists a P such that $\trden{s} = P$ and either: 
(a) $P \treduces \tstr{s}$ and $S \sreduces \strin{s}$, and $s \in lang{r}$; or
(b) $P \err$ and $S \err$.
\end{thm}

\begin{proof}
The proof proceeds by induction on the typing relation for $S$ and an appropriate
choice of $P$; in each case, the choice is obvious. The subcases (a) proceed
by inversion and appeals to the induction hypothesis. The subcases (b) proceed
by the standard error propagation rules omitted for space.
Throughout the proof, properties from the closure lemma for regular languages
are necessary.

%\begin{description}
%\item[S-T-String-I:] 
%Let $S = \rstr{s}$ and suppose $\sctx \vdash \rstr{s} : \stringin{r}$.
%Choose $T = \str{s}$ and note that $\trden{S} = P$ by Tr-String.
%By P-E-String, $P \treduces \str{s}$ and by S-E-String $S \treduces \rstr{s}$.
%Finally, by inversion of S-T-Stringin-I, $s \in \lang{r}$.
%
%\item[S-T-Concat:]
%Let $S = \rconcat{S_1}{S_2}$ and suppose $\sctx \vdash S : \stringin{r_1 r_2}$.
%By inversion, $\sctx \vdash S_1 : \stringin{r_1}$.
%It follows by induction that there exists a $P_1$ such that $\trden{S_1} = P_1$.
%By a similar argument for $S_2$ and $r_2$, there exists a $P_2$ such that $\trden{S_2} = P_2$.
%Choose $P = \concat{P_1}{P_2}$.
%
%We first prove property (a).
%Note that $S_1$ and $P_1$ do not result in errors and that $S_1$ is well typed.
%Therefore, $S_1 \sreduces \rstr{s_1}$ and $P_1 \treduces \str{s_1}$ for some $s_1 \in \lang{r_1}$ by theorems 8 and 9 respectively. % TODO-nrf make sure this numbering is correct
%Similarly, $S_2 \sreduces \rstr{s_2}$ and $P_2 \treduces \str{s_2}$ for some $s_2 \in \lang{r_2}$.
%Therefore, $S \sreduces \rstr{s_1 s_2}$ by S-E-Concat and $\concat{P_1}{P_2} \treduces \str{s_1 s_2}$ by P-E-Concat.
%Finally, $s_1s_2 \in \lang{r_1}{r_2}$ by \ref{thm:regexprops}.
%
%Consider property (b).
%If $S_1 \err$ then $P_1 \err$ by induction, and it follows that $S \err$ and $P \err$ by respective error propagation rules.
%Similarly, if $S_2 \err$ then $P_2 \err$ and it follow that $S \err$ and $P \err$ by induction and propagation.
%
%\item[S-T-Replace:]
%Let $S = \rreplace{r}{S_1}{S_2}$ and suppose $\sctx \vdash S : \stringin{r'}$ for some $s$.
%By inversion of S-T-Replace, , $\sctx S_1 : \stringin{r_1}$ and $\sctx : \stringin{r_2}$ 
%such that $\lsubst{r}{r_1}{r_2} = r'$.
%By induction, there exists some $P_1, P_2$ such that $\trden{S_1} = P_1$, $\trden{S_2} = P_2$
%and either (a) or (b) holds.
%
%If (a) holds then $S_1 \sreduces \rstr{s_1}$ and $P_1 \treduces \str{s_1}$ for some $s_1 \in \lang{r_1}$,
%and similarly for $S_2, P_2$ and some $s_2 \in \lang{r_2}$.
%Therefore, by S-E-Replace, $S \sreduces \rstr{s}$ for some $s = \lreplace{r}{s_1}{s_2}$.
%Choose $P = \preplace{r}{s_1}{s_2}$.
%By a similar argument and P-E-Replace, $P \treduces \str{s}$ for some $s = \lreplace{r}{s_1}{s_2}$.
%What remains to be shown is $\lreplace{r}{s_1}{s_2} \in \lang{\lsubst{r}{r_1}{r_2}}$,
%which follows from Leamm D since $s_1 \in r_1$ and $s_2 \in r_2$.
%
%If (b) holds for $S_1$ and $P_1$, then $S \err$ and $P \err$ by propagation rules.
%Similarly, if (b) hols for $S_2$ and $P_2$ then $S \err$ and $P \err$ by propagation rules.
%
%\item[S-T-Coerce:]
%Let $S = \rcoerce{r}{S'}$ and suppose $\sctx \vdash \rcoerce{r}{S} : \stringin{r}$.
%By inverstion $\Psi \vdash S' : \stringin{r'}$ for an arbitrary $r'$.
%By induction there exists a $P'$ such that $\trden{S'} = P'$ and either (a) or (b)
%holds for $S'$ and $P'$.
%
%If (a) holds then $S' \sreduces \rstr{s'}$ and $P' \treduces \str{s'}$ for some $s' \in \lang{r'}$.
%Note that either $s' \in \lang{r}$ or $s' \not \in \lang{r}$ by property 2 of \ref{thm:regexprops}.
%Suppose $s' \in \lang{r}$. Then $\rcoerce{r}{S} \sreduces \rstr{S'}$ by S-E-Coerce.
%Choose $P = \check{\rx{r}}{P'}$ and note that $P \treduces \str{s'}$ by P-E-Coerce.
%Now suppose $s' \not \in \lang{r}$. Then $S \err$ and $P \err$ by P-E-Check-Err
%and S-E-Coerce-Err.
%
%Finally, if (b) holds then $S \err$ and $P \err$ by propagation.
%
%\end{description}
\end{proof}

@@

\section{Conclusion}

Composable analyses which complement existing approaches constitute a promising approach toward the integration of security concerns into programming languages.
In this paper, we presented a system with both of these properties and defined a security-prserving transformation.
Unlike other approaches, our solution complements existing, familiar solutions while providing a strong guarantee that traditiona library and framework-based approaches are implemented and utilized correctly.
